Poll-Based Forecasting of the 2024 U.S. Presidential Election

### 2024-11-04 paper/paper_draft_1.qmd
Update paper_draft_1.qmd
Update conclusion and discussion

Overall, our approach demonstrates how feature engineering and predictive modeling can offer insights into candidate support based on the available data. However, it is important to interpret these results cautiously, as they rely on specific variables and assumptions embedded within the dataset. In this analysis, we aggregated representative feature values for each candidate by using the mean or median for numeric variables, the mode for categorical variables, and the most frequent occurrence for Boolean values. Further refinement and additional data could enhance the robustness of these predictions, contributing to a more comprehensive forecast in future studies.

# Discussion {#sec-discussion}

This paper presents a predictive analysis of voter support for 2024 U.S. presidential candidates Kamala Harris and Donald Trump. Using a “poll-of-polls” approach, it integrates polling data from diverse sources, emphasizing reliability, sample size, and methodology. Linear and Bayesian models were applied to improve prediction accuracy.

The analysis provides two key insights. First, our model predicts a slight advantage for Kamala Harris, with a support estimate of 47.6% compared to Donald Trump’s 43.5%, indicating a competitive but narrow lead. Second, it underscores the impact of poll reliability on predictive accuracy. Traditional methods like live phone surveys show greater accuracy than online methods, reinforcing the importance of reliability-weighted data in improving forecast precision.

>>>>

The results indicate that high transparency scores and reliable polling methods improve prediction quality, while careful attention to demographic representation—such as sample size and population type—ensures the polling data reflects the broader electorate. The model forecasts a slight lead for Kamala Harris, with an estimated 47.6% support compared to 43.5% for Donald Trump, underscoring the essential role of reliable data sources in public opinion forecasting. These findings highlight the importance of stringent polling standards and precise demographic selection in enhancing the predictive accuracy of electoral models.

# Discussion

This study employs a multiple linear regression model to analyze polling data and forecast public support for U.S. 2024 presidential election candidates Kamala Harris and Donald Trump. By identifying key determinants of polling accuracy, this analysis predicts a slight lead for Kamala Harris with 47.6% support over Donald Trump’s 43.5%.

Findings reveal that transparency and demographic representation are essential to reliable election forecasts. Polls with higher transparency scores yield more accurate predictions, emphasizing the importance of clear polling practices. Sample size and population type variations also underscore the need for representative sampling to capture genuine voter sentiment.
